---
title: "Course Project: Shiny Application and Reproducible Pitch"
author: "Tingfen Yan"
date: "9/3/2017"
output: ioslides_presentation
---
##Course Project
  -This is the final presentation for the Course Project of the "Development data products" course
  
  -This project includes two activities:
   
   1. Create a Shiny application
  
   2. Create a presentation in Slidify or Rstudio Presenter to pitch for the application.

##Shiny application
  -explore data set by two different graphs
  
  -one is box plot and one is feature plot
  
  -I am using iris dataset to finish this assignment

Some information for this dataset
```{r echo=FALSE}
data(iris)
head(iris)
```

##graphs
-feature plot
```{r echo=FALSE, message=FALSE, warning=FALSE}
library(caret)
```

```{r echo=FALSE}
featurePlot(x=iris[,1:4],y=iris[,5],plot="pairs")
```

The plot colored by species

##Data
  -The app developed for the first part of the assignment demo is avalilable at: http://rpubs.com/yanRpubs/304193

  -Source code for ui.R and server.R files are available on the GitHub repo: https://github.com/OpenIDUser6/OpenIDUser6.github.io
